---
title: "Practising Certificates"
output: 
  flexdashboard::flex_dashboard:
    theme:
      version: 4
      bootswatch: materia
    orientation: rows
    vertical_scroll: fill
    self_contained: false
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(DT)
library(plotly)
library(tidymodels)

certificate_database <- readRDS("database/certificate_database.rds") %>%
  mutate(
    status = case_when(
      (first_date >= max(last_date)-28) & (first_date > min(first_date)) ~ "new",
      (last_date >= max(last_date)-28) & (last_date < max(last_date)) ~ "expired",
      TRUE ~ "unchanged"
      ),
    certificate = case_when(
      certificate == "Scheme Actuary" ~ "Scheme",
      certificate == "Chief Actuary (non-Life with Lloyd's)" ~ "Non-Life with Lloyd's", 
      certificate == "Lloyd's Syndicate Actuary" ~ "Syndicate",
      certificate == "Chief Actuary (Life)" ~ "Life",
      certificate == "With Profits Actuary" ~ "With Profits",
      certificate == "Chief Actuary (Life, Non-Directive)" ~ "Life (Non-Directive)",
      certificate == "Chief Actuary (non-Life without Lloyd's)" ~ "Non-Life ex Lloyd's",
      TRUE ~ "unknown"
    ),
    certificate = factor(
      certificate, levels = c(
        "Life",
        "Life (Non-Directive)",
        "With Profits",
        "Non-Life with Lloyd's",
        "Non-Life ex Lloyd's",
        "Syndicate",
        "Scheme"
        )
      ),
    fellow_type = factor(fellow_type, levels = c("Fellow FIA", "Fellow FFA"))
    )

current_certificates <- 
  certificate_database %>%
  filter(last_date >= max(last_date)-1)

new_certificates <-
  certificate_database %>%
  filter(status == "new")

expired_certificates <-
  certificate_database %>%
  filter(status == "expired")

num_current_certificates <- current_certificates %>% nrow()
num_new_certificates <- new_certificates %>% nrow()
num_expired_certificates <- expired_certificates %>% nrow()
num_cera <- current_certificates %>% filter(cera == TRUE) %>% nrow()
num_ffa <- current_certificates %>% filter(fellow_type == "Fellow FFA") %>% nrow()
num_certificate_holders_by_certificate <-
  current_certificates %>% 
  group_by(certificate) %>% 
  summarise(count = n(), .groups = "drop")

all_new_certificates <- 
  certificate_database %>% 
  filter(first_date > min(first_date))

all_expired_certificates <-
  certificate_database %>%
  filter(last_date < max(last_date)-1)

axis_first_date <- as.Date("2022-08-01")
axis_last_date <- Sys.Date()

linear_model_new_certificates <-
  linear_reg() %>% 
  set_engine("lm") %>% 
  set_mode("regression") %>%
  fit(qualification_year ~ first_date, data = all_new_certificates) 

linear_model_expired_certificates <-
  linear_reg() %>% 
  set_engine("lm") %>% 
  set_mode("regression") %>%
  fit(qualification_year ~ last_date, data = all_expired_certificates) 

dates_to_model <- 
  tibble(
    first_date = seq(from = axis_first_date, to = axis_last_date, by = 1),
    last_date = first_date
    )

predict_qualification_year_new <-
  linear_model_new_certificates %>%
  predict(dates_to_model) %>%
  rename(modelled_qualification_year_new = `.pred`)
  

predict_qualification_year_expired <-
  linear_model_expired_certificates %>%
  predict(dates_to_model) %>% 
  rename(modelled_qualification_year_expired = `.pred`)

model_results <- bind_cols(
  dates_to_model, 
  predict_qualification_year_new,
  predict_qualification_year_expired)
```

Summary
===================================== 

Gauges and value boxes
-------------------------------------

### last updated
```{r}
valueBox(
  certificate_database$last_date %>% max(), 
  icon = "fa-calendar-alt"
  )
```

### current certificates issued
```{r}
valueBox(
  num_current_certificates, 
  icon = "fa-medal"
  )
```

### new certificates issued in last 30 days
```{r}
valueBox(
  num_new_certificates, 
  icon = "fa-plus-circle"
  )
```

### certificates expired in last 30 days
```{r}
valueBox(
  num_expired_certificates, 
  icon = "fa-minus-circle"
  )
```

Main charts {.tabset}
-------------------------------------


### Certificates by qualification year
```{r}
current_certificates %>%
  group_by(certificate, fellow_type, qualification_year, cera) %>%
  summarise(count = n(), .groups = "drop") %>%
  plot_ly(
    x = ~qualification_year,
    y = ~count,
    type = "bar",
    color = ~certificate
  ) %>%
  layout(
    barmode = "stack"
  )
```

### CERA split by certificate
```{r}
current_certificates %>%
  group_by(certificate, cera) %>%
  summarise(count_cera = n(), .groups = "drop") %>%
  left_join(num_certificate_holders_by_certificate, by = "certificate") %>%
  mutate(proportion = 100 * count_cera / count) %>%
  plot_ly(
    y = ~proportion,
    x = ~certificate,
    color = ~cera,
    type = "bar"
  ) %>%
  layout(
    barmode = "stack",
    legend = list(orientation = 'h')
  )
```

> Currently, `r num_cera` certificates belong to person with CERA.

### FFA/FIA split by certificate
```{r}
current_certificates %>%
  group_by(certificate, fellow_type) %>%
  summarise(count_fellow_type = n(), .groups = "drop") %>%
  left_join(num_certificate_holders_by_certificate, by = "certificate") %>%
  mutate(proportion = 100 * count_fellow_type / count) %>%
  plot_ly(
    y = ~proportion,
    x = ~certificate,
    color = ~fellow_type,
    type = "bar"
  ) %>%
  layout(
    barmode = "stack",
    legend = list(orientation = 'h')
  )
```

> Currently, `r num_ffa` certificates belong to persons that are FFA Fellows.

### New certificates
```{r}
model_results %>%
  left_join(all_new_certificates, by = c("first_date")) %>%
  group_by(first_date, qualification_year) %>%
  summarise(
    count = n(), 
    linear_regression = mean(modelled_qualification_year_new), 
    .groups = "drop"
    ) %>%
  plot_ly(
    x = ~first_date,
    y = ~qualification_year,
    type = "scatter",
    mode = "markers",
    #color = ~count,
    size = ~count,
    name = "new certificates"
  ) %>%
  layout(
    xaxis = list(range = c(axis_first_date, axis_last_date)),
    showlegend = FALSE
  ) %>%
  add_trace(
    x = ~first_date,
    y = ~linear_regression,
    name = "regression",
    mode = "lines",
    alpha = 1
  )
```

### Expired certificates
```{r}
model_results %>%
  left_join(all_expired_certificates, by = c("last_date")) %>%
  group_by(last_date, qualification_year) %>%
  summarise(
    count = n(), 
    linear_regression = mean(modelled_qualification_year_expired), 
    .groups = "drop"
    ) %>%
  plot_ly(
    x = ~last_date,
    y = ~qualification_year,
    type = "scatter",
    mode = "markers",
    #color = ~count,
    size = ~count,
    name = "expired certificates"
  ) %>%
  layout(
    xaxis = list(range = c(axis_first_date, axis_last_date)),
    showlegend = FALSE
  ) %>%
  add_trace(
    x = ~last_date,
    y = ~linear_regression,
    name = "regression",
    mode = "lines",
    alpha = 1
  )
```



Tables
=====================================

Main tables {.tabset}
-------------------------------------

### Certificate changes (last 30 days)
```{r}
new_certificates %>%
  bind_rows(expired_certificates) %>%
  DT::datatable(style = "auto")
```

### Regulatory record
```{r}
certificate_database %>%
  filter(regulatory_record == TRUE) %>%
  DT::datatable(style = "auto")
```

### Database

```{r}
DT::datatable(
  certificate_database,
  filter = list(position = 'top', clear = FALSE),
  style = "auto"
  )
```
