---
title: "Practising Certificates"
output: 
  flexdashboard::flex_dashboard:
    theme:
      version: 4
      bootswatch: materia
    orientation: rows
    vertical_scroll: fill
    self_contained: false
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(DT)
library(plotly)

certificate_database <- readRDS("database/certificate_database.rds") %>%
  mutate(
    status = case_when(
      (first_date >= max(last_date)-28) & (first_date > min(first_date)) ~ "new",
      (last_date >= max(last_date)-28) & (last_date < max(last_date)-1) ~ "expired",
      TRUE ~ "unchanged"
      ),
    certificate = case_when(
      certificate == "Scheme Actuary" ~ "Scheme",
      certificate == "Chief Actuary (non-Life with Lloyd's)" ~ "Non-Life with Lloyd's", 
      certificate == "Lloyd's Syndicate Actuary" ~ "Syndicate",
      certificate == "Chief Actuary (Life)" ~ "Life",
      certificate == "With Profits Actuary" ~ "With Profits",
      certificate == "Chief Actuary (Life, Non-Directive)" ~ "Life (Non-Directive)",
      certificate == "Chief Actuary (non-Life without Lloyd's)" ~ "Non-Life ex Lloyd's",
      TRUE ~ "unknown"
    ),
    certificate = factor(
      certificate, levels = c(
        "Life",
        "Life (Non-Directive)",
        "With Profits",
        "Non-Life with Lloyd's",
        "Non-Life ex Lloyd's",
        "Syndicate",
        "Scheme"
        )
      ),
    fellow_type = factor(fellow_type, levels = c("Fellow FIA", "Fellow FFA"))
    )

current_certificates <- 
  certificate_database %>%
  filter(last_date >= max(last_date)-1)

new_certificates <-
  certificate_database %>%
  filter(status == "new")

expired_certificates <-
  certificate_database %>%
  filter(status == "expired")

num_current_certificates <- current_certificates %>% nrow()
num_new_certificates <- new_certificates %>% nrow()
num_expired_certificates <- expired_certificates %>% nrow()
num_cera <- current_certificates %>% filter(cera == TRUE) %>% nrow()
num_ffa <- current_certificates %>% filter(fellow_type == "Fellow FFA") %>% nrow()
num_certificate_holders_by_certificate <-
  current_certificates %>% 
  group_by(certificate) %>% 
  summarise(count = n(), .groups = "drop")


```

Summary
===================================== 

Gauges and value boxes
-------------------------------------

### last updated
```{r}
valueBox(
  certificate_database$last_date %>% max(), 
  icon = "fa-calendar-alt"
  )
```

### current certificates issued
```{r}
valueBox(
  num_current_certificates, 
  icon = "fa-medal"
  )
```

### new certificates issued in last 30 days
```{r}
valueBox(
  num_new_certificates, 
  icon = "fa-plus-circle"
  )
```

### certificates expired in last 30 days
```{r}
valueBox(
  num_expired_certificates, 
  icon = "fa-minus-circle"
  )
```

Main charts {.tabset}
-------------------------------------


### Certificates by qualification year
```{r}
current_certificates %>%
  group_by(certificate, fellow_type, qualification_year, cera) %>%
  summarise(count = n(), .groups = "drop") %>%
  plot_ly(
    x = ~qualification_year,
    y = ~count,
    type = "bar",
    color = ~certificate
  ) %>%
  layout(
    barmode = "stack"
  )
```

### CERA split by certificate
```{r}
current_certificates %>%
  group_by(certificate, cera) %>%
  summarise(count_cera = n(), .groups = "drop") %>%
  left_join(num_certificate_holders_by_certificate, by = "certificate") %>%
  mutate(proportion = 100 * count_cera / count) %>%
  plot_ly(
    y = ~proportion,
    x = ~certificate,
    color = ~cera,
    type = "bar"
  ) %>%
  layout(
    barmode = "stack",
    legend = list(orientation = 'h')
  )
```

> Currently, `r num_cera` certificates belong to person with CERA.

### FFA/FIA split by certificate
```{r}
current_certificates %>%
  group_by(certificate, fellow_type) %>%
  summarise(count_fellow_type = n(), .groups = "drop") %>%
  left_join(num_certificate_holders_by_certificate, by = "certificate") %>%
  mutate(proportion = 100 * count_fellow_type / count) %>%
  plot_ly(
    y = ~proportion,
    x = ~certificate,
    color = ~fellow_type,
    type = "bar"
  ) %>%
  layout(
    barmode = "stack",
    legend = list(orientation = 'h')
  )
```

> Currently, `r num_ffa` certificates belong to persons that are FFA Fellows.

### New certificates
```{r}
certificate_database %>%
  filter(first_date > min(first_date)) %>%
  group_by(qualification_year, first_date) %>%
  summarise(count = n()) %>%
  plot_ly(
    x = ~first_date,
    y = ~qualification_year,
    type = "scatter",
    mode = "markers",
    color = ~count,
    size = ~count
  )
```

### Expired certificates
```{r}
certificate_database %>%
  filter(last_date < max(last_date)) %>%
  group_by(qualification_year, last_date) %>%
  summarise(count = n()) %>%
  plot_ly(
    x = ~last_date,
    y = ~qualification_year,
    type = "scatter",
    mode = "markers",
    color = ~count,
    size = ~count
  )
```



Tables
=====================================

Main tables {.tabset}
-------------------------------------

### Certificate changes (last 30 days)
```{r}
new_certificates %>%
  bind_rows(expired_certificates) %>%
  DT::datatable(style = "auto")
```

### Regulatory record
```{r}
certificate_database %>%
  filter(regulatory_record == TRUE) %>%
  DT::datatable(style = "auto")
```

### Current certificates

```{r}
DT::datatable(
  certificate_database,
  filter = list(position = 'top', clear = FALSE),
  style = "auto"
  )
```
